Supplementary Materials

### 2022-12-28 manuscript/supplementary.tex
more ms updates

\section{The Background Selection Models}

Under the background selection model, the diversity in window $b$ is $\bar{\pi}(b,
\Psi) = \bar{B}(b, \Psi) \pi_0$. Here, $\bar{B}(b | \Psi)$ is the predicted
reduction in diversity due to BGS in window $b$, given background selection
parameters $\Psi$. In practice, we pre-calculate $\bar{B}(x | \Psi)$ at fixed
sites $x$ across the genome, and take the average of the fixed sites $B$ values
within widow $b$ for the average $\bar{B}(b | \Psi)$.

BGS models assume multiplicative fitness effects across sites. Thus, the total
reduction due to segments across the genome is the product of the individual
reductions,

@@

@@

\subsection{Calculation of the classic BGS B Maps}

The classic BGS model expresses the reduction for a focal site in the middle of
a segment \parencite{Hudson1995-xc,Hudson1994-oh,Nordborg1996-nq}; here we
consider a focal site directly to an arbitrary side of a segment under a
deleterious mutations, and extend the model to handle a focal segment
arbitrarily far from the segment. Using our notation from equation
\eqref{suppeqn:b}, the classic mutation-selection-balance BGS model is,

>>>>

\section{The Generalized Background Selection Models}

Under the generalized background selection models used in our likelihood, the
diversity in window $b$ is $\bar{\pi}(b, \Psi) = \bar{B}(b, \Psi) \pi_0$. Here,
$\bar{B}(b | \Psi)$ is the predicted reduction in diversity due to BGS in
window $b$, given background selection parameters $\Psi$. In practice, we
pre-calculate $B(x | \Psi)$ at fixed sites $x$ across the genome, and take the
average of the fixed sites $B$ values within widow $b$ for the average
$\bar{B}(b | \Psi)$.

GBGS models assume multiplicative fitness effects across sites. Thus, the total
reduction due to segments across the genome is the product of the individual
reductions,

@@

\subsection{Reductions Under the Classic BGS Model}

The classic BGS model, which assumes deleterious mutations cannot fix,
expresses the reduction for a focal site in the middle of a segment
\parencite{Hudson1995-xc,Hudson1994-oh,Nordborg1996-nq}; here we consider a
focal site directly to an arbitrary side of a segment under a deleterious
mutations, and extend the model to handle a focal segment arbitrarily far from
the segment. Using our notation from equation \eqref{suppeqn:b}, the classic
mutation-selection-balance BGS model is,

\subsection{Reduction Under the Modified Santiago and Caballero Model}

When weak deleterious mutations can fix, causing substitutions, the classic
background selection models break down. We find that the generalized background
selection model of \textcite{Santiago2016-mu} works well (see Section XXX for
our derivation). We describe how we use the models here.

\subsection{Discretization of Parameters}

@@
